---
title: "Kolleg Europa - Network Analysis"
subtitle: "Datenauswertung Reisediplomatie-Netzwerk"
author: "Stefan Haussner"
date: "7 März 2019"
output: html_document
---

```{r setup, include=FALSE, eval = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(igraph)
library(threejs)
library(DT)
```

Examining both types of nodes in a two-mode network graphic is often the first
step in studying an affiliation network. However, it is also useful to examine the
direct connections among the nodes of one type at a time. 

This can be done by extracting and visualizing the one-mode projections
of the two-mode affiliation network. Every actor by event affiliation network can
produce two one-mode networks, one of actors and one of the events or affiliations.

The bipartite.projection function returns a list of two igraph network objects. The first network is made up of the direct ties among the first mode, and the second network shows the ties among the second mode.

```{r eval=FALSE}
rd_projection <- bipartite.projection(rd_igraph)
rd_projection


rd_hosts <- rd_projection$proj1
rd_eu28 <- rd_projection$proj2
```

```{r eval=FALSE}
plot.igraph(rd_eu28)
```

# Analyse des EU28-Netzwerks

Das EU28-Netzwerk ist ein Co-occurence Netzwerk. Zwei Länder der EU28 haben dann eine Verbindung, wenn sie das gleiche Gastland besucht haben. Das Netzwerk ist ein ungerichtetes Netzwerk.

## Paths

Die Länder die am wenigsten gemeinsame Besuchsländer hatten.

```{r eval=FALSE}
farthest_vertices(rd_eu28)
```

## Welche Länder sind im Netzwerk besonders auffallend?

It makes intuitive sense that a network member who is connected to many other
members of the network is in a prominent position. For non-directed networks, we
will say that this type of actor has high centrality, or that it is in a central position.
However, there are a number of ways of operationalizing this type of prominence.
In fact, there are dozens of centrality statistics available to the network analyst.

### Degree centrality

The simplest measure of centrality by far is based on the notion that a node that
has more direct ties is more prominent than nodes with fewer or no ties. Degree
centrality thus, is simply the degree of each node.

```{r eval=FALSE}
r_degree <- degree(rd_eu28)/vcount(rd_eu28)


data.frame(r_degree)

plot.igraph(rd_eu28,
            vertex.size = r_degree*20)
```

### Closeness Centrality

Instead of examining only the direct connections of the nodes, we can focus on how
close each node is to every other node in a network. This leads to the concept of
closeness centrality, where nodes are more prominent to the extent they are close to
all other nodes in the network.

```{r eval=FALSE}
r_closeness <- closeness(rd_eu28)
data.frame(r_closeness)
```



### Betweenness
Welche Knoten müssen am häufigsten durchlaufen werden. Betweenness centrality measures the extent that a node sits ‘between’ pairs of other
nodes in the network, such that a path between the other nodes has to go through
that node. A node with high betweenness is prominent, then, because that node is in
a position to observe or control the flow of information in the network.

```{r eval=FALSE}
r_betweenness <- igraph::betweenness(rd_eu28)
data.frame(r_betweenness)
```

Alle Ergebnisse gesammelt und in sortierbarer Tabelle:

```{r results='asis'}
data_frame(r_degree,r_closeness,r_betweenness) %>% round(digits = 4) %>% knitr::kable()
```
